The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
Minor change to FThresholds paper
Minor changes to abstract of FThresholds

\author[]{Emily E.\ Witt}
\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
\email{witt@ku.edu}
\thanks{E.E.~Witt was partially supported by NSF DMS \#1623035.}
\date{\today}

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
\end{abstract}

>>>>

\author[]{Emily E.\ Witt}
\address{Department of Mathematics, University of Kansas, Lawrence, KS~66045, USA}
\email{witt@ku.edu}
\thanks{E.~E.~Witt was partially supported by NSF DMS \#1623035.}
\date{\today}

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants used to study singularities in positive characteristic.
\end{abstract}
